Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
edits

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| c | l | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24 \\
2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38 \\
3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12 \\
4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39 \\
5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85 \\
6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85 \\
7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15 \\
8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9.18\,s & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8.98\,s & \xmark & \xmark \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}

>>>>

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| c | l | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24\,s \\
2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38\,s \\
3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12\,s \\
4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39\,s \\
5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85\,s \\
6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85\,s \\
7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15\,s \\
8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9.18\,s & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8.98\,s & \xmark & \xmark \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}
